preparation

### 2025-04-14 data/preparation.Rmd
updated data cleaning, wrangling, and other thesis-prep

```{r setup}
library(tidyverse)

# Read in data
child <- read_csv("child.csv", col_names = TRUE)
parent <- read_csv("parent.csv", col_names = TRUE)
```

@@

# age discrepancies
false_age <- youtube %>% 
  select(age_match, bday, P_age, age, transaction_id) %>% 
  filter(age_match == FALSE) %>% 
  mutate(age = as.numeric(age)) %>% 
  mutate(difference = abs(P_age - age)) %>% 
  mutate(large_diff = ifelse(
    difference > 1,
    TRUE,
    FALSE
  )) %>% 
  filter(large_diff == TRUE) %>% 
  select(transaction_id)

# write_csv(false_age, "transaction_ids.csv")
```

```{r youtube wrangling}
# Time Scores
```

```{r youtube composites}
### Recoding factor variables as numeric variables to create aggregate scores
youtube <- youtube %>% 
  mutate(
    across(c(`homophily_appear_1`, `homophily_appear_2`, `homophily_appear_3`, `homophily_appear_4`, `homophily_appear_5`, `homophily_behave_1`, `homophily_behave_2`, `homophily_behave_3`, `homophily_behave_4`, `homophily_behave_6`, parasocial_1, parasocial_2, parasocial_3, parasocial_4, parasocial_5),
           ~ recode (.,
                     "Really disagree" = 1,
                     "Disagree" = 2,
                     "I don't know" = 3,
                     "Agree" = 4,
                     "Really agree" = 5
           ))) %>% 
  mutate(
    across(c(malleable_1, malleable_2, malleable_3, malleable_4),
           ~ recode(.,
                    "Really disagree" = 1,
                    "Disagree" = 2,
                    "Neither agree nor disagree" = 3,
                    "Agree" = 4,
                    "Really agree" = 5
           ))) %>%  
  mutate(
    across(c(regularities_1, regularities_2, regularities_3, regularities_4, regularities_5, regularities_6, regularities_7),
           ~ recode(.,
                    "Really disagree" = 1,
                    "Disagree" = 2,
                    "Neither agree nor disagree" = 3,
                    "Agree" = 4,
                    "Really agree" = 5
           ))) %>%  
  select(-c(homophily_behave_5))

@@

# Parasocial relationship scores (each block separately, then aggregate)
youtube <- youtube %>% 
  # homophily-appear -- total possible score = 20
  mutate(h_appear_score = rowSums(across(homophily_appear_1:homophily_appear_5))) %>% 
  # homophily-behave -- total possible score = 20
  mutate(h_behave_score = rowSums(across(homophily_behave_1:homophily_behave_6))) %>% 
  # parasocial -- total possible score = 20
  mutate(parasocial_score = rowSums(across(parasocial_1:parasocial_5))) %>% 
  #Composite scores
  mutate(composite = rowSums(across(h_appear_score:parasocial_score))) %>% 
  # Proportion scores
  mutate(h_appear_score = h_appear_score/20) %>%
  mutate(h_behave_score = h_behave_score/20) %>%
  mutate(parasocial_score = parasocial_score/20) %>%
  mutate(composite = composite/60)

# Racial regularities score (behavior) -- total possible score = 35
youtube <- youtube %>% 
  # Reverse coded items
  mutate(across(c(regularities_3, regularities_5, regularities_7), ~ 6 - .)) %>% 
  # Score
  mutate(regularity_score = rowSums(across(regularities_1:regularities_7))) %>% 
  mutate(regularity_score = regularity_score/35)
```

```{r}
# H1: time spent on YouTube and children’s observation of racial regularities covary
```

```{r}
# H2: if children spend more time on YouTube, they will display greater racial stereotyping and prejudice against outgroups
```

```{r}
# H3: the relationship between children’s time spent on YouTube and their exhibited racial stereotyping and prejudice will be mediated by their observations of negative racial regularities
```

```{r}
# H4: the relationship between the amount of time that children spend on YouTube and their racial stereotyping and prejudice will be moderated by whether they have a parasocial relationship with a favorite YouTuber of a race other than their own
```

>>>>

```{r setup}
library(psych)
library(knitr)
library(broom)
library(papaja)
library(mediation)
library(tidyverse)

# Read in data
child <- read_csv("child.csv", col_names = TRUE)
parent <- read_csv("parent.csv", col_names = TRUE)
child_old <- read_csv("child_old.csv", col_names = TRUE)
parent_old <- read_csv("parent_old.csv", col_names = TRUE)
```

```{r label}
# Marking new data with "1"
child$new_sample <- ifelse(child$transaction_id %in% child_old$transaction_id, 0, 1)
parent$new_sample <- ifelse(parent$transaction_id %in% parent_old$transaction_id, 0, 1)
```

@@

# age discrepancies
youtube <- youtube %>% 
  # age as numeric
  mutate(age = as.numeric(age)) %>% 
  # add column measuring difference in responses
  mutate(difference = abs(P_age - age)) %>% 
  mutate(large_diff = ifelse(
    difference > 1,
    TRUE,
    FALSE
  ))

sum(youtube$large_diff)

summary(youtube$age)

```

```{r youtube wrangling}
# Time Scores

# Parent time report
youtube <- youtube %>% 
  mutate(Pdays = ifelse(Pdays == "None", 0, Pdays)) %>% 
  mutate(Pdays = str_sub(Pdays, start = 1, end = 1)) %>%
  mutate(Ptime = as.character(Ptime)) %>% 
  mutate(Ptime = dplyr::recode(Ptime,
                        "0 minutes" = 0,
                        "15 minutes or less" = 1,
                        "30 minutes or less" = 2,
                        "45 minutes or less" = 3,
                        "1 hour or less" = 4,
                        "1.5 hours or less" = 5,
                        "2 hours or less" = 6,
                        "More than 2 hours" = 7,
                        # Only 1 instance of other; participant listed 2 (presumably 2 hours)
                        "Other" = 6
                        )) %>% 
  mutate(Pdays = as.numeric(Pdays)) %>%
  mutate(Ptime = as.numeric(Ptime)) %>%
  mutate(Ptime_score = Pdays * Ptime)

# Survey logic was "If 1 AND 2 were selected, show next block" - about 9 responses
# Just using parent data
```

```{r time binned}
youtube <- youtube %>% 
  mutate(Ptime_max = case_when(
                        Ptime == "0" ~ 0,
                        Ptime == "1" ~ 0.25,
                        Ptime == "2" ~ 0.5,
                        Ptime == "3" ~ 0.75,
                        Ptime == "4" ~ 1,
                        Ptime == "5" ~ 1.5,
                        Ptime == "6" ~ 2,
                        Ptime == "7" ~ 3,
                        TRUE ~ NA_real_
                        )) %>% 
  mutate(Ptime_max = as.numeric(Ptime_max)) %>%
  mutate(Ptime_max_score = Pdays * Ptime_max)
```

```{r time correlation}
# Degree to which parent and child reports of time are correlated

# Youtube correlation with all responses, parent replacing 10 -- 0.9319548
# Correlating parent and child data for responses of 3-7 days -- 0.9168719
x <- youtube %>%
  mutate(days = str_sub(days, start = 1, end = 1)) %>%
  filter(!(days %in% c(1, 2))) %>% 
cor(youtube$Pdays, youtube$days, method = "pearson")

# see correlation in Ctime - 0.732496
test <- youtube %>%
  filter(!(days %in% c(1, 2, "N"))) %>% 
  mutate(Ctime = case_when(
    Ctime == "0 minutes" ~  0,
    Ctime == "15 minutes or less" ~ 1,
    Ctime == "30 minutes or less" ~ 2,
    Ctime == "45 minutes or less" ~ 3,
    Ctime == "1 hour or less" ~ 4,
    Ctime == "1.5 hours or less" ~ 5,
    Ctime == "2 hours or less" ~ 6,
    Ctime == "More than 2 hours" ~ 7,
    TRUE ~ NA_real_)) %>% 
  mutate(Ctime = as.numeric(Ctime)) %>% 
  mutate(time_match = ifelse(Ctime == Ptime,
                             1, 0)) %>% 
  select(Ptime, Pdays, Ctime, days, time_match) %>%
  mutate(diff = abs(Ptime - Ctime)) %>% 
  mutate(large_diff = ifelse(diff > 2,
    TRUE,
    FALSE))
sum(test$large_diff)
cor(test$Ptime, test$Ctime, method = "pearson")
# Use parent values as primary predictor; report correlation for responses

# Consider how to report time scores in writing 
summary(youtube$Ptime)
```

```{r youtube composites}
### Recoding factor variables as numeric variables to create aggregate scores
youtube <- youtube %>% 
  mutate(
    across(c(`homophily_appear_1`, `homophily_appear_2`, `homophily_appear_3`, `homophily_appear_4`, `homophily_appear_5`, `homophily_behave_1`, `homophily_behave_2`, `homophily_behave_3`, `homophily_behave_4`, `homophily_behave_6`, parasocial_1, parasocial_2, parasocial_3, parasocial_4, parasocial_5),
           ~ dplyr::recode (.,
                     "Really disagree" = 1,
                     "Disagree" = 2,
                     "I don't know" = 3,
                     "Agree" = 4,
                     "Really agree" = 5
           ))) %>% 
  mutate(
    across(c(malleable_1, malleable_2, malleable_3, malleable_4),
           ~ dplyr::recode(.,
                    "Really disagree" = 1,
                    "Disagree" = 2,
                    "Neither agree nor disagree" = 3,
                    "Agree" = 4,
                    "Really agree" = 5
           ))) %>%  
  mutate(
    across(c(regularities_1, regularities_2, regularities_3, regularities_4, regularities_5, regularities_6, regularities_7),
           ~ dplyr::recode(.,
                    "Really disagree" = 1,
                    "Disagree" = 2,
                    "Neither agree nor disagree" = 3,
                    "Agree" = 4,
                    "Really agree" = 5
           ))) %>%  
  select(-c(homophily_behave_5))

@@

# Parasocial relationship scores (each block separately, then aggregate)
youtube <- youtube %>% 
  # homophily-appear -- total possible score = 25
  mutate(h_appear_score = rowSums(across(homophily_appear_1:homophily_appear_5))) %>% 
  # homophily-behave -- total possible score = 25
  mutate(h_behave_score = rowSums(across(homophily_behave_1:homophily_behave_6))) %>% 
  # parasocial -- total possible score = 25
  mutate(parasocial_score = rowSums(across(parasocial_1:parasocial_5))) %>% 
  #Composite scores
  mutate(composite = rowSums(across(h_appear_score:parasocial_score))) %>% 
  # Proportion scores
  mutate(h_appear_score = h_appear_score/25) %>%
  mutate(h_behave_score = h_behave_score/25) %>%
  mutate(parasocial_score = parasocial_score/25) %>%
  mutate(composite = composite/75)

# Racial regularities score (behavior) -- total possible score = 35
youtube <- youtube %>% 
  # Reverse coded items
  mutate(across(c(regularities_3, regularities_5, regularities_7), ~ 6 - .)) %>% 
  # Score
  mutate(regularity_score = rowSums(across(regularities_1:regularities_7))) %>% 
  mutate(regularity_score = regularity_score/35)

# presenting raw data can contextualize the data - make sure to say that 1.0 is highly fixed, eg, and 0.5 is neutral
```

```{r friend cleaning}
# Friend Choice cleaning

# Splitting multiple races
youtube <- youtube %>%
  separate(race_ethnicity, into = c("race_1", "race_2", "race_3"), sep = ",\\s*")

# Recoding kid race and gender based on method design
youtube <- youtube %>% 
  # Trim "kid"
  mutate(friend = str_extract(friend, "\\d+")) %>%  
  # Add gender
  mutate(friend_gender = case_when(
    friend %in% c(1, 3, 5, 7, 9)  ~ "Male",
    friend %in% c(2, 4, 6, 8, 10) ~ "Female",
    TRUE ~ as.character(friend)
    )) %>% 
  # Recode based on race
  mutate(friend_race = case_when(
    friend %in% c(1, 4)  ~ "Black or African American",
    friend %in% c(2, 9)  ~ "White",
    friend %in% c(3, 6)  ~ "Hispanic or Latino/a",
    friend %in% c(5, 8)  ~ "South Asian",
    friend %in% c(7, 10)  ~ "Asian",
    TRUE ~ as.character(friend)
    ))

# Matches
# Race match = 1, race does not match = 2, race not represented = 3
youtube <- youtube %>% 
  mutate(race_match = case_when(
    race_1 %in% c("American Indian or Alaska Native", "Middle Eastern or North African", "Native Hawaiian or Other Pacific Islander", "Some Other Race", "Multiracial") ~ 2,
    friend_race == race_1 ~ 1, 
    friend_race != race_1 ~ 0,
    TRUE ~ NA_real_
  )) %>% 
  mutate(race_match_binary = ifelse(race_match == 1, 1, 0)) %>% 
  relocate(race_1, .after = friend_race) %>% 
  # gender match
  mutate(gender_match = ifelse(
    friend_gender == gender,
    1, 0
  ))
```

```{r}
write_csv(youtube, "youtube.csv")
```

```{r}
# YouTuber cleaning

favorite <- youtube %>% 
  dplyr::select(favorite, transaction_id)

write_csv(favorite, "favorite.csv")
```

```{r demographic descriptives }
# Descriptive statistics - demographics

# Age
ggplot(data = youtube) +
  aes(x = age) + 
  geom_bar(color = "black", fill = "grey")

# Race
ggplot(data = youtube) +
  aes(x = race_1) + 
  geom_bar(color = "black", fill = "grey")

# Gender
ggplot(data = youtube) +
  aes(x = gender) + 
  geom_bar(color = "black", fill = "grey")
```

```{r time descriptives}
# Descriptive statistics - time

# Histogram of parent reported time spent on YouTube
ggplot(data = youtube) +
  aes(x = Pdays) + 
  geom_bar(color = "black", fill = "grey")

# Histogram of parent reported days per week spent on YouTube
ggplot(data = youtube) +
  aes(x = Ptime) + 
  geom_bar(color = "black", fill = "grey")

# Histogram of parent time score spent on YouTube
ggplot(data = youtube) +
  aes(x = Ptime_score) + 
  geom_bar(color = "black", fill = "grey")

# Histogram of parent time score spent on YouTube - minutes as opposed to scores
ggplot(data = youtube) +
  aes(x = Ptime_max_score) + 
  geom_bar(color = "black", fill = "grey")

ggplot(data = youtube) +
  aes(x = Ptime_score) +
  geom_boxplot()
summary(youtube$Ptime_score)

ggplot(data = youtube) +
  aes(x = race_1) +
  geom_bar()

```

```{r regularity descriptive}
# Regularities
ggplot(data = youtube) +
  aes(x = regularity_score) + 
  geom_bar(color = "black", fill = "grey")

ggplot(data = youtube) +
  aes(x = regularity_score) + 
  geom_boxplot(color = "black", fill = "grey")

summary(youtube$regularity_score)

sd(youtube$regularity_score)
# t.test

# Negative outgroup prejudice overall 
# run t test for just white kids alone?

t.test(youtube$regularity_score, mu = 0.5)
```

```{r}
# variance relative to t test
individual_means <- rowMeans(youtube[, paste0("regularities_", 1:7)], na.rm = TRUE)

# Center scores around the target mean
centered <- individual_means - 2.572143

# Variance
variance <- mean(centered^2)

# Standard deviation
std_dev <- sqrt(variance)

variance
std_dev
```

```{r}
# Alpha

# Created with ChatGPT help
# Function which returns Cronbach's alpha
return_alpha <- function(data, cols) {
  # select data 
  selected_data <- data %>% select(all_of(cols))
  # compute alpha
  alpha_result <- psych::alpha(selected_data, check.keys = TRUE)
  # Extract and return the raw alpha value
  return(alpha_result$total$raw_alpha)
}

# Creating a list of all measures, grouped by questionnaire
measures <-
  list(
  "Group Malleability" = c("malleable_1", "malleable_2", "malleable_3", "malleable_4"),
  "Homophily (Appearance)" = c("homophily_appear_1", "homophily_appear_2", "homophily_appear_3", "homophily_appear_4", "homophily_appear_5"),
  "Homophily (Appearance)" = c("homophily_behave_1", "homophily_behave_2", "homophily_behave_3", "homophily_behave_4", "homophily_behave_6"),
  "Parasociality" = c("parasocial_1", "parasocial_2", "parasocial_3", "parasocial_4", "parasocial_5"),
  "Racial Regularities" = c("regularities_1", "regularities_2", "regularities_3", "regularities_4", "regularities_5")
)

# Creating data frame with measures and corresponding alpha
reliability <- data.frame(
  Measure = names(measures),
  Alpha = sapply(measures, function(cols) return_alpha(youtube, cols))
)

# Adding column with evaluations of alpha
reliability <- reliability %>%
  mutate(Alpha = round(Alpha, digits = 2)) %>% 
  mutate(
    Evaluation = case_when(
      Alpha >= 0.95 ~ "Excellent",
      Alpha >= 0.9 ~ "Great",
      Alpha >= 0.8 ~ "Good",
      Alpha >= 0.7 ~ "Acceptable",
      Alpha >= 0.6 ~ "Questionable",
      Alpha < 0.6 ~ "Poor"
    )
  )

# Generate table
kable(reliability, 
      align = c("c", "c", "c"),
      # Setting caption here
      caption = "Reliability (assessed through Cronbach's Alpha) of questionnaires used, within sample") %>% 
  kable_styling(position = "center", latex_options = c("striped"))
```

```{r}
# report regression function
report_regression <- function(model) {

  # Extract coefficients and p-values
  m_glance <- glance(model)
  # Format the p-value
  p_value <- apa_p(m_glance$p.value, add_equals = TRUE)
  # Create a string with the results
  report <- paste0("$F$(", 
                   m_glance$df, 
                   ", ", m_glance$df.residual, 
                   ") = ", round(m_glance$statistic, 2), 
                   ", $p$ ", p_value,
                   ", $R^2$ = ", round(m_glance$r.squared, 2))
  # Return report
  return(report)    
}
```

```{r}
# report regression coefficients function
report_coefficients <- function(model){
  m_tidy <- tidy(model) %>%
    filter(term != "(Intercept)") %>%
    mutate(
      report = paste0(
        "$B$ = ", round(estimate, 2),
        ", $SE$ = ", round(std.error, 2),
        ", $p$ ", apa_p(p.value, add_equals = TRUE)
      ))

  return(m_tidy$report)
}
```

```{r}
# H1: time spent on YouTube and children’s observation of racial regularities covary

# Add age and gender

# Use ptime as primary predictors

lm_h1 <- lm(regularity_score ~ Ptime_max_score + age + gender + race_1, data = youtube)
summary(lm_h1)

report_regression(lm_h1)
report_coefficients(lm_h1)

# testing things 
t.test(regularity_score ~ gender, data = youtube)
# Male participants only
t_male <- t.test(youtube$regularity_score[youtube$gender == "Male"], mu = 0.5)
# Female participants only
t_female <- t.test(youtube$regularity_score[youtube$gender == "Female"], mu = 0.5)
t_male
t_female
# male scores are significantly different from a neutral score but females are not

 # add age as covariate

ggplot(data = youtube) +
  aes(x = Ptime_max_score, y = regularity_score) +
  geom_point() +
  stat_smooth(method = "lm")

# why is this data so flat?
# gender, race, state
```

```{r}
# H2: if children spend more time on YouTube, they will display greater racial stereotyping against outgroups
# Make sure that measure is strongly connected to construct in writing

lm_h2 <- lm(malleable_score ~ Ptime_max_score, data = youtube)
summary(lm_h2)
report_regression(lm_h2)
report_coefficients(lm_h2)
```

```{r}
#ns time*gender interaction
declan_model <- lm(malleable_score ~ Ptime_max_score*gender, data = youtube)
drop1(declan_model, test = "Chisq")
#ns time*age interaction
declan_model2 <- lm(malleable_score ~ Ptime_max_score*age, data = youtube)
drop1(declan_model2, test = "Chisq")
#sig predict of gender
declan_model3 <- glm(malleable_score ~ gender, data = youtube)
drop1(declan_model3, test = "Chisq")

ggplot(data = youtube) +
  aes(x = Ptime_score, y = malleable_score) +
  geom_point() +
  stat_smooth(method = "loess")

t.test(malleable_score ~ gender, data = youtube)
t.test(regularity_score ~ gender, data = youtube)
```

```{r}
# Genre anovas 
aov1 <- aov(malleable_score ~ genre, data = youtube)
summary(aov1)

aov2 <- aov(regularity_score ~ genre, data = youtube)
summary(aov2)

ggplot(data = youtube) +
  aes(x = genre) + 
  geom_bar(color = "black", fill = "grey")

```

```{r}
# H3: the relationship between children’s time spent on YouTube and their exhibited racial stereotyping and prejudice will be mediated by their observations of negative racial regularities

# Add age and gender

lm_h3 <- lm(malleable_score ~ regularity_score, data = youtube)
summary(lm_h3)

# Mediation model
# Mediator model (regularity ~ time)
model.M <- lm(regularity_score ~ Ptime_max_score, data = youtube)
# Outcome model (malleable ~ time + regularity)
model.Y <- lm(malleable_score ~ Ptime_max_score + regularity_score, data = youtube)
med.out <- mediate(model.M, model.Y, treat = "Ptime_max_score", mediator = "regularity_score", boot = TRUE, sims = 1000)
summary(med.out)

ggplot(data = youtube) +
  aes(x = regularity_score, y = malleable_score) +
  geom_point() +
  stat_smooth(method = "lm")
```

```{r}
# H4: the relationship between the amount of time that children spend on YouTube and their racial stereotyping and prejudice will be moderated by whether they have a parasocial relationship with a favorite YouTuber of a race other than their own

# If you have a strong relationship with a white youtuber compared to Other - how does this drive racial - most kids put white youtubers as their favorite youtuber, so wanted to see how parasocials with white youtubers are driving the effect

# Add age and gender

lm_h4 <- lm(malleable_score ~ composite, data = youtube)
summary(lm_h4)

# plotting composite
ggplot(data = youtube) +
  aes(x = composite, y = malleable_score) +
  geom_point() +
  stat_smooth(method = "lm")
# plotting each component individually
ggplot(data = youtube) +
  aes(x = h_appear_score, y = malleable_score) +
  geom_point() +
  stat_smooth(method = "lm")
ggplot(data = youtube) +
  aes(x = h_behave_score, y = malleable_score) +
  geom_point() +
  stat_smooth(method = "lm")
ggplot(data = youtube) +
  aes(x = parasocial_score, y = malleable_score) +
  geom_point() +
  stat_smooth(method = "lm")

# controlling for age, effect holds

# effect of genre - check frequencies first, then mean comparisons, then anova (fixed/mixed effects?)
# race of Youtuber/particular youtuber
```

```{r yter race}
# Favorite YouTuber race
favorite_coded <- read.csv("favorite_coded.csv")

# Cleaning 
favorite_youtuber <- inner_join(favorite_coded, youtube, by = join_by(transaction_id)) %>% 
  rename(yt_gender = Gender) %>% 
  rename(yt_race = Race.1) %>% 
  rename(favorite_yt = favorite.x)
favorite_youtuber <- favorite_youtuber %>% 
  dplyr::select(favorite_yt, YouTuber, yt_gender, yt_race, gender, race_1, age, Ptime_max_score, malleable_score, regularity_score, h_appear_score, h_behave_score, parasocial_score, composite, race_match_binary)

favorite_youtuber <- favorite_youtuber %>% 
  mutate(YouTuber = replace_na(YouTuber, "None")) %>% 
  mutate(yt_match = ifelse(
    yt_race == race_1,
    1, 0)) %>% 
  mutate(yt_match_all = case_when(
    yt_match == 1 ~ "Match",
    yt_match == 0 ~ "Mismatch",
    TRUE ~ "None"
  )) %>% 
  mutate(mrbeast = ifelse(
    YouTuber == "MrBeast",
    1, 0)) %>% 
  mutate(yt_white = ifelse(
    yt_race == "White",
    1, 0
  ))

# Mean centering for regression
favorite_youtuber <- favorite_youtuber %>%
  mutate(
    composite_centered = composite - 0.5,
    regularity_centered = regularity_score - 0.5,
    malleable_centered = malleable_score - 0.5
  )

write.csv(favorite_youtuber, "favorite_youtuber.csv")
```

```{r yter race}
# Descriptive
ggplot(data = favorite_youtuber) +
  aes(x = yt_race) + 
  geom_bar(color = "black", fill = "grey")

yt_match_mod <- glm(yt_match ~ Ptime_max_score + age + gender, data = favorite_youtuber, family = binomial)
summary(yt_match_mod)

t.test(Ptime_max_score ~ mrbeast, data = favorite_youtuber) # significant
t.test(composite ~ mrbeast, data = favorite_youtuber) # not significant
t.test(malleable_score ~ mrbeast, data = favorite_youtuber) # not significant
t.test(regularity_score ~ mrbeast, data = favorite_youtuber) # not significant
# look at subset of mrbeast = fave
sum(favorite_youtuber$mrbeast) # 42; is power enough? can we make a meaningful comparison with only 42? look into this
# mr beast is unique sample - not that he's racist in particular, just that this is a pattern that has emerged

# avg age
# avg time 
mrbeast_df <- favorite_youtuber %>% 
  filter(YouTuber == "MrBeast") 
# time
mean(mrbeast_df$Ptime_max_score)
# skewed right
ggplot(data = mrbeast_df) +
  aes(x = Ptime_max_score) + 
  geom_bar(color = "black", fill = "grey")
# age
mean(mrbeast_df$age) # mean = 11.2
ggplot(data = mrbeast_df) +
  aes(x = age) + 
  geom_bar(color = "black", fill = "grey")
# gender
ggplot(data = mrbeast_df) +
  aes(x = gender) + 
  geom_bar(color = "black", fill = "grey")

# do kids who watch all white youtubers show greater prejudice? fixed beliefs? 
t.test(malleable_score ~ yt_white, data = favorite_youtuber) # not significant
t.test(regularity_score ~ yt_white, data = favorite_youtuber) # not significant
```

```{r friend choice}
# Race and friend choice

# Logistic regression for race match vs no race match - does amount of time on YouTube predict friend choice 
# then address gender later

logit <- youtube %>% 
  filter(race_match != 2)

match <- glm(race_match_binary ~ Ptime_max_score + age + gender, data = youtube, family = binomial)
summary(match)

# Does race match predict malleability, regularity, or composite? 
match2 <- glm(malleable_score ~ race_match_binary, data = youtube, family = binomial)
summary(match2)
match3 <- glm(regularity_score ~ race_match_binary, data = youtube, family = binomial)
summary(match3)
match4 <- glm(composite ~ race_match_binary, data = youtube, family = binomial)
summary(match4)

t.test(malleable_score ~ race_match_binary, data = youtube)
t.test(regularity_score ~ race_match_binary, data = youtube)
t.test(composite ~ race_match_binary, data = youtube)

#Do predict malleability, regularity, or composite predict race match? 
match2 <- glm(race_match_binary ~ malleable_score, data = youtube, family = binomial)
summary(match2)
match3 <- glm(race_match_binary ~ regularity_score, data = youtube, family = binomial)
summary(match3)
match4 <- glm(race_match_binary ~ composite, data = youtube, family = binomial)
summary(match4)

ggplot(logit) +
  aes(x = Ptime_max_score, y = race_match) +
  geom_point(position = position_jitter(height = 0.05), alpha = 0.5) +
  geom_smooth(method = "glm", method.args = list(family = "binomial"), 
              formula = y ~ x, se = TRUE)

binom.test(x = sum(youtube$race_match == 1),
           n = nrow(youtube),
           p = 0.5,
           alternative = "greater")  # Use "two.sided" if you're testing any difference

```

```{r}
# Exploratory:
# Parent opinion
```

```{r}
library(boot)

# Your data: df
# Predictors: time_youtube, racial_regularities
# Outcome: racial_attitudes

# Define bootstrap function
boot_fn <- function(data, indices) {
  d <- data[indices, ]  # resample
  model <- lm(malleable_score ~ Ptime_max_score + regularity_score, data = youtube)
  return(coef(model)[c("Ptime_max_score", "regularity_score")])
}

# Run bootstrap
set.seed(123)
results <- boot(data = youtube, statistic = boot_fn, R = 1000)

# Extract bootstrap coefficients
boot_coefs <- results$t  # matrix: rows = bootstraps, columns = coefficients

# Calculate covariance
cov(boot_coefs[, 1], boot_coefs[, 2])
```

```{r}
library(mediation)

model.m <- lm(regularity_score ~ gender, data = youtube)
model.y <- lm(malleable_score ~ gender + regularity_score, data = youtube)

med_output <- mediate(model.m, model.y, treat = "gender", mediator = "regularity_score", boot = TRUE)
summary(med.out)

# Extract estimates
acme   <- round(med.out$d0, 3)
ade    <- round(med.out$z0, 3)
total  <- round(med.out$tau.coef, 3)
propmed <- round(med.out$n0, 2)

# Extract p-values (formatted APA-style)
acme_p  <- ifelse(med.out$d0.p < .001, "< .001", paste0("= ", round(med.out$d0.p, 3)))
ade_p   <- ifelse(med.out$z0.p < .001, "< .001", paste0("= ", round(med.out$z0.p, 3)))
total_p <- ifelse(med.out$tau.p < .001, "< .001", paste0("= ", round(med.out$tau.p, 3)))
propmed_p <- ifelse(med.out$n0.p < .001, "< .001", paste0("= ", round(med.out$n0.p, 3)))

```

```{r}
library(DiagrammeR)

grViz(sprintf("
digraph mediation {

  graph [layout = dot, rankdir = LR]

  node [shape = box, fontsize = 10, width = 1.1, style = solid]

  X [label = 'IV\\n(gender)']
  M [label = 'Mediator\\n(regularity_score)']
  Y [label = 'DV\\n(malleable_score)']

  edge [fontsize = 10]

  X -> M [label = 'a = %.3f\\np %s']
  M -> Y [label = 'b (implied)']
  X -> Y [label = 'c′ = %.3f\\np %s']

  # Add total and proportion mediated as a note
  node [shape = plaintext, fontsize = 9]
  info [label = 'Total effect = %.3f (p %s)\\nProportion mediated = %.2f (p %s)']
  info -> Y [style = invis]
}
", acme, acme_p, ade, ade_p, total, total_p, propmed, propmed_p))
```

```{r}
# 1. Group difference only
t.test(malleable_score ~ gender, data = youtube)

# 2. Simple regression
a <- lm(malleable_score ~ gender, data = youtube)
summary(a)

# 3. With racial regularities added
b <- lm(malleable_score ~ gender + regularity_score, data = youtube)
summary(b)
```

```{r}
# Favorite YouTuber and regularity

# Anova
anov2 <- aov(regularity_score ~ yt_match_all, data = favorite_youtuber)
summary(anov2)
TukeyHSD(anov2)

# Regression
lrp_centered <- lm(regularity_score ~ yt_match_all * composite_center + malleable_center, data = favorite_youtuber)
summary(lrp_centered)

# Plot
ggplot(data = favorite_youtuber) +
  aes(x = composite, y = regularity_score) +
  facet_wrap(~ yt_match_all) +
  stat_smooth(method = "lm", color = "#800000", linewidth = 0.8, fill = "lightgrey") +
  geom_point() +
  my_theme()  
```

```{r}
# max
max_time <- youtube %>% 
  filter(Ptime_max_score > 15)

maxtest <- lm(malleable_score ~ Ptime_max_score, data = youtube)
summary(maxtest)

maxtest2 <- lm(regularity_score ~ Ptime_max_score, data = youtube)
summary(maxtest2)
```
```{r}
#| label: fig-youtuber-descriptive
#| fig-cap: "Distributions of race/ethnicity of participants and their self-reported favorite YouTubers"
#| layout-ncol: 2
#| fig-height: 6

# Stacking two plots
par(mfrow = c(1, 2))

# Plot 1: Distribution of participant race/ethnicity
ggplot(favorite_youtuber) +
  aes(x = race_1) +
  geom_bar(fill = "darkgrey", color = "black") + 
  scale_y_continuous(breaks = seq(from = 0, to = 90, by = 15),
                     limits = c(0, 90)) +
  labs(x = "Race/Ethnicity", y = "Count",
       title = "Participant Race/Ethnicity") +
  theme(axis.text.x = element_text(angle = 30, hjust = 1)) +
  my_theme()

# Plot 2: Distribution of favorite youtuber race/ethnicity
ggplot(favorite_youtuber) +
  aes(x = yt_race) +
  geom_bar(fill = "darkgrey", color = "black") + 
  scale_y_continuous(breaks = seq(from = 0, to = 90, by = 15),
                     limits = c(0, 90)) +
  labs(x = "Race/Ethnicity", y = "Count",
       title = "Race/Ethnicity of Children's Favorite YouTubers") +
  theme(axis.text.x = element_text(angle = 30, hjust = 1)) +
  my_theme()
```

```{r}
# gender
lm1 <- lm(composite ~ gender, data = favorite_youtuber)
summary(lm1)
lm2 <- lm(composite ~ gender + yt_match_all, data = favorite_youtuber)
summary(lm2)
lm3 <- lm(composite ~ gender * yt_match_all, data = favorite_youtuber)
summary(lm3)
lm4 <- lm(regularity_score ~ gender, data = favorite_youtuber)
summary(lm4)

combined_model <- lm(malleable_score ~ gender + yt_match_all + composite + regularity_score, data = favorite_youtuber)
summary(combined_model)

# Gender as mediator
# Step 1: Mediator model
med_model1 <- lm(composite ~ gender, data = favorite_youtuber)
# Step 2: Outcome model (DV predicted by mediator + gender)
out_model1 <- lm(malleable_score ~ composite + gender, data = favorite_youtuber)
# Run mediation analysis
med_out1 <- mediate(med_model1, out_model1, treat = "gender", mediator = "composite", boot = TRUE)

# Mediator model
med_model2 <- lm(regularity_score ~ gender, data = favorite_youtuber)
# Outcome model
out_model2 <- lm(malleable_score ~ regularity_score + gender, data = favorite_youtuber)
# Mediation
med_out2 <- mediate(med_model2, out_model2, treat = "gender", mediator = "regularity_score", boot = TRUE)

summary(med_out1)
summary(med_out2)

```
